### 2019-04-10 paper/paper.tex
updated bib

To better visualize the status of inter-package dependencies, we constructed
a directed dependency graph using dependants as out-degrees and
dependencies as in-degrees. Based on this dependency graph, Figure \ref{outDegree}
displays the percentage of packages with various amounts of dependencies. 
[MIGHT NEED TO CHANGE BASED ON DATA: While the average number of dependencies 
of packages continues to increase, the percentage of packages with zero 
to three dependencies has actually increased since the end of the original paper's
reporting period \cite{Wittern:2016}. This suggests some changes to developer 
behaviour, likely either as a deliberate effort by programmers seeking to avoid the perils of 
complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
ways in which JavaScript is used for project development.

@@

\begin{figure*}
  % \includegraphics[width=.5\textwidth]{figures/highest_ranked_monthly_100.pdf}

  \includegraphics[width=1\textwidth]{figures/highest_ranked_monthly_100.pdf}
  \caption{Neat you can include PDFs}
  \label{ranksByYear}
\end{figure*}

@@

@@

@@

@@

  \bibitem{Wittern:2016}
  Erik Wittern, Philippe Suter, and Shriram Rajagopalan.
  \newblock A look at the dynamics of the javascript package ecosystem.
  \newblock In {\em Proceedings of the 13th International Conference on Mining
    Software Repositories}, MSR '16, pages 351--361, New York, NY, USA, 2016.
    ACM.

  \end{thebibliography}

>>>>

To better visualize the status of inter-package dependencies, we constructed
a directed dependency graph using dependants as out-degrees and
dependencies as in-degrees. Based on this dependency graph, Figure \ref{outDegree}
displays the percentage of packages with various amounts of dependencies. 
[MIGHT NEED TO CHANGE BASED ON DATA: While the average number of dependencies 
of packages continues to increase, the percentage of packages with zero 
to three dependencies has actually increased since the end of the original paper's
reporting period \cite{Wittern:2016}. This suggests some changes to developer 
behaviour, likely either as a deliberate effort by programmers seeking to avoid the perils of 
complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
ways in which JavaScript is used for project development. [ADD EXACT VALUES]

In addition to the number of external dependencies per package, 
we investigate how packages support dependants. The original paper 
discovered that the majority of in degrees are concentrated among a core 
minority of packages, with the majority of packages having no dependants,
a discovery that has also been observed in other software ecosystems such
as Linux and MySQL \cite{Myers:2003}. In our updated data, we discover 
that not only have these aspects held true, but the concentration of 
dependencies has actually increased. As of April 1\textsuperscript{st} 2019, [NUMBER]\% of packages
had zero dependants, up from [NUMBER]\% in 2015. Meanwhile, only \%[NUMBER] of packages
had 6 or more dependants, down from \%[NUMBER] in September 2015. It is again interesting to note
that the current trend of increasing concentration appears to have begun shortly after the end of window in the original
paper \cite{Wittern:2016}.

@@

@@

\begin{figure*}
  \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
  \caption{\code{npm} rank (based on PageRank) of five packages with the lowest geometric mean per year}
  \label{ranksByYear}
\end{figure*}

@@

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/select_packages.png}
  \caption{\code{npm} rank (PageRank) over time of selected utility packages}
  \label{selectPackages}
\end{figure}

@@

  \bibitem{Myers:2003}
  Christopher~R. Myers.
  \newblock Software systems as complex networks: Structure, function, and
    evolvability of software collaboration graphs.
  \newblock {\em Phys. Rev. E}, 68:046116, Oct 2003.

@@

  \bibitem{Wittern:2016}
  Erik Wittern, Philippe Suter, and Shriram Rajagopalan.
  \newblock A look at the dynamics of the javascript package ecosystem.
  \newblock In {\em Proceedings of the 13th International Conference on Mining
    Software Repositories}, MSR '16, pages 351--361, New York, NY, USA, 2016.
    ACM.
  \end{thebibliography}
